On the Functionality of the Multilayer Perceptron

### 2020-11-15 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be  modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, which can be modeled by the boundary conditions:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

\paragraph*{}In order to specify a solution, we must also specificy two intitial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
\begin{equation}
U(x,0) = f(x) 
	\text{\hspace*{2cm} and \hspace*{2cm}}
\frac{\partial U}{\partial t}(x,0) = g(x)
\end{equation}
Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms. For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck. $g(x)$

@@

@@

\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a representation of how overtones and energy is distributed in the signal's frequency domain. As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row. This encodes the FCM for a single analysis frame (in frequency-space) in the waveform. For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
\begin{equation}
\label{eqn-FeatureFCM}
\text{FCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
\end{equation}
We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
\begin{equation}
FCM = \sum_{i=0}^{k'} \frac{1}{k'}\text{FCM}_{i}\big[ s^{(i)} \big]
\end{equation}

@@

\paragraph*{}The optimization of neural networks are heavily dependent on initial conditions of parameters and the data sets. We consider models that suffer from this phenomenon to be \textit{high-variance} models \cite{James}. To eliminate any concerns of possible out-liers, or abnormalities that arise, it is commont implement a resampling method called \textit{cross validation} (Also called X-val) \cite{Geron,Goodfellow}. This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets. $1$ subset is reserved to evaluate the model, and $K-1$ remaining subsets are used to train the model. For each of the $K$ models, we can evaluate a series of performance metrics, and store any model parameters. We can compare any one model to the other $K-1$ models to ensure that each network is performing consistently, despite small changes in the initial data set. We detail pseudo-code for a $K$-Fold Cross Validation algorithm.

@@

\paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data. Each model $F^*$, shows one possible outcome of training the network. It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq. (\ref{eqn-Theta}) that it uses to make any predictions.

>>>>

\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$. The string is flexible, and free to vibrate in a single dimension. We describe the state of string over space and time with a function $U(x,t)$. The behavior of the string can be  modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
\begin{equation}
\label{eqn-1DWaveEqn}
\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
\end{equation}
Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, with the nut at $x = 0$ and the bridge at $x = L$, which can be modeled by the boundary conditions:
\begin{equation}
U(0,t) = 0 
	\text{\hspace*{2cm} and \hspace*{2cm}}
U(L,t) = 0 
\end{equation}

\paragraph*{}In order to specify a solution, we must also specify two initial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
\begin{equation}
U(x,0) = f(x) 
	\text{\hspace*{2cm} and \hspace*{2cm}}
\frac{\partial U}{\partial t}(x,0) = g(x)
\end{equation}
Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms. For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck. $g(x)$

@@

\paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.

@@

\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a representation of how overtones and energy is distributed in the signal's frequency domain. As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row. This encodes the FCM for a single analysis frame (in frequency-space) in the waveform. For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
\begin{equation}
\label{eqn-FeatureFCM}
\text{FCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
\end{equation}
We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
\begin{equation}
FCM = \frac{1}{k'}\sum_{i=0}^{k'}\text{FCM}_{i}\big[ s^{(i)} \big]
\end{equation}

@@

\paragraph*{}The optimization of neural networks are heavily dependent on initial conditions of parameters and the data sets. We consider models that suffer from this phenomenon to be \textit{high-variance} models \cite{James}. To eliminate any concerns of possible out-liers, or abnormalities that arise, it is common to implement a resampling method called \textit{cross validation} (Also called X-validation) \cite{Geron,Goodfellow}. This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets. $1$ subset is reserved to evaluate the model, and $K-1$ remaining subsets are used to train the model. For each of the $K$ models, we can evaluate a series of performance metrics, and store any model parameters. We can compare any one model to the other $K-1$ models to ensure that each network is performing consistently, despite small changes in the initial data set. We detail pseudo-code for a $K$-Fold Cross Validation algorithm.

@@

\paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data. Each model $F^*$, shows a possible outcome of training the network given a subset of data samples, and a particular set of initial parameters.. It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq. (\ref{eqn-Theta}) that it uses to make any predictions.
